Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage

### 2024-09-22 paper/paper.qmd
final paper

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Lexun Yu
thanks: "Code and data are available at: [https://github.com/yulexun/toronto-fire](https://github.com/yulexun/toronto-fire)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

@@

In this paper we visualize Toronto's Fire Incidents data.

# Data

@@

@@

## Fire Protection Equipments

@@

# Discussion

@@

The Toronto Fire Service (TFS) generally has efficient response times, averaging about 4.9 minutes, as noted in the summary statistics (@tbl-clean-tfs-summary-1). Over the period from 2013 to 2023, response times varied between 5 and 10 minutes, with some notable outliers, according to @fig-clean-tfs-diff-dollar-time-1. This indicates that while TFS usually responds quickly, there can be occasional delays due to outside factors. Importantly, these response times do not lead to significant financial losses, because the relationship between response time and financial impact is weak, as indicated by @fig-response-vs-money. This implies that for the TFS, rapid response to fire incidents is not the most critical factor. Other elements, such as the severity of the fire and existing fire protection measures, are more decisive in determining the financial consequences of fire events.

>>>>

---
title: "Assessing Fire Response Efficiency and the Crucial Role of Protection Systems in Reducing Damage"
subtitle: "Insights from Toronto’s Fire Incidentsfinal"
author: 
  - Lexun Yu
thanks: "Code and data are available at: [https://github.com/yulexun/toronto-fire](https://github.com/yulexun/toronto-fire)."
date: today
date-format: long
abstract: "This paper analyzes fire incidents in Toronto between 2013 and 2023, focusing on the response times of the Toronto Fire Service (TFS) and the impact of fire protection systems. The study finds that TFS usually responds within 5 to 10 minutes, but the correlation between response time and financial losses is weak, and other factors like fire protection equipment play a larger role in mitigating damage. Fire alarms and sprinkler systems in present and operational reduce losses significantly. This research the importance of maintaining fire protection systems and improving fire service efficiency to enhance urban fire safety."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

@@

In this paper we visualize Toronto's Fire Incidents data. The remainder of the paper is structured as follows. [Section 2](#sec-data) discusses the raw and cleaned data, as well as the summary statistic. Then in [Section 2.2](#sec-data-tfs) and [Section 2.3](#sec-data-fpe), We discuss the trend and distribution of TFS response time and fire protection equipment presence. In [Section 3](#sec-discuss), we provide analysis of the trend and correlation in [Section 2](#sec-data), as well as the limitations and future directions in resolving urban fire incidents.

# Data {#sec-data}

@@

## Toronto Fire Service Responsiveness {#sec-data-tfs}

@@

## Fire Protection Equipments {#sec-data-fpe}

@@

# Discussion {#sec-discuss}

@@

The Toronto Fire Service (TFS) generally has efficient response times, averaging about 4.9 minutes, as noted in the summary statistics [@tbl-clean-tfs-summary-1]. Over the period from 2013 to 2023, response times varied between 5 and 10 minutes, with some notable outliers, according to @fig-clean-tfs-diff-dollar-time-1. This indicates that while TFS usually responds quickly, there can be occasional delays due to outside factors. Importantly, these response times do not lead to significant financial losses, because the relationship between response time and financial impact is weak, as indicated by @fig-response-vs-money. This implies that for the TFS, rapid response to fire incidents is not the most critical factor. Other elements, such as the severity of the fire and existing fire protection measures, are more decisive in determining the financial consequences of fire events.
